
%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[runningheads,a4paper]{llncs}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
%\usepackage{comment}
\usepackage{tikz}
\usepackage{float}
%%\usepackage{subfig}
\usepackage{url}
\usepackage{todonotes}
\usepackage{float}
\usepackage{courier}

%\usepackage{subfloat}
\usepgflibrary{arrows}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,fit}
\usetikzlibrary{shapes.geometric}
\usepgflibrary{shapes.geometric}
\usetikzlibrary{shapes.symbols}
\usepgflibrary{shapes.callouts}
\usetikzlibrary{shapes.callouts}


\usetikzlibrary{through} 
\include{railway_tikz_macros}
 
\lstset{basicstyle=\fontsize{8}{8}\ttfamily, xleftmargin=2em, framexleftmargin=1.5em, framexrightmargin=-0.6em, frame=single}

\begin{document}
\mainmatter 

\title{Towards Safety Analysis of ERTMS/ETCS \\ Level 2 in Real-Time
  Maude}

\titlerunning{ERTMS/ETCS Level 2 in Real-Time Maude}

\author{Phillip James\inst{1} \and Andrew Lawrence \inst{2} \and \\ 
Markus Roggenbach\inst{1} \and  Monika Seisenberger\inst{1}}
%
\institute{Swansea University, UK
\and
Hitachi Data Systems, Poole, UK.
}

\authorrunning{James, Lawrence, Roggenbach, Seisenberger}

\maketitle

\begin{abstract}
ERTMS/ETCS is a European signalling, control and train protection
system. In this paper, we model and analyse this complex system of
systems, including its hybrid elements, on the design level in
Real-Time Maude. Our modelling allows us to formulate safety
properties in physical rather than in logical terms. %% For instance ``no
%% collision between trains'' is expressed as the physical invariant: the
%% distance (in meters) between trains never falls below a minimum
%% threshold.
We systematically validate our model by simulation and error
injection. Using the Real-Time Maude model-checker, we effectively
verify a number of small rail systems.
\end{abstract}

\input{introduction.tex}
%% Markus

\input{ertms.tex}
%% Phil

\input{maude.tex}
%%% Andy -- Include time/mte/delta
%%% Uli has subsection on completeness.

\input{modelling.tex}
%%% Monika -- Comment on Generic.


\input{validation.tex}
%%% Monika -- Simulation
%%% Phil -- Error Injection
%%% Uli -- Completeness

\input{modelchecking.tex}
%%% Phil

\input{relatedwork.tex}
%%% Todo: Markus

\input{summary.tex}
%%% Todo: Markus

\paragraph{Acknowledgement} 
The authors would like to thank Simon Chadwick, Siemens Rail
Automation, UK, for his continued support and many helpful
discussions. We also appreciate the helpful advice from  Peter \"Olveczky
%towards our modelling 
on Real-Time Maude and the constructive comments given by three anonymous referees. Finally, we thank Erwin R.\ Catesbeiana (Jr) for timely hints on how to
stay on track.

\bibliographystyle{abbrv}
\bibliography{doc}

\end{document}

