\section{Modelling ERTMS in Maude}

To the best of our knowledge, our modelling of ERTMS is the first one
comprising all ERTMS subsystems required for the control cycle in
ERTMS/ETCS Application Level 2, c.f.\ Figure 6 in the ERTMS/ETCS
System Requirements Specification \cite{spec}. For simplicity, we
consider only uni-directional rail yards, as these exhibit many of the
components of bi-directional rail yards, but are of a lower complexity
with regards to the number of routes required within the model. Also,
we make the standard assumption that trains have no length. This is
the typical abstraction when one deals with trains whose length is
shorter than any track length in the given scheme plan. For a detailed
discussion of the topic see, e.g., our publication discussing train
length \cite{JamesMNRST14}.

In the following, we provide an overview of our model%
\footnote{The models are available at:\\
{\tt \footnotesize
 http://www.cs.swan.ac.uk/\%7Ecsmarkus/ProcessesAndData/Models}}: first we discuss the static
data types; then we look at the instantaneously reacting
sub-systems, i.e., controller, interlocking, and RBC; next, we
describe how we capture  train behaviour, which requires
differential equations describing motion; finally, we address how to
express collision-freedom. We note that our model is generic, with only
location specific data as a parameter. This location specific data has been encoded manually, however this process could be automated within OnTrack~\cite{james14c}.

%% {\sl For the purpose of reviewing, our models are available at
%% \begin{center}
%% \url{http://www.cs.swan.ac.uk/%7Ecsmarkus/Station.zip}.
%% \end{center}
%% The \%7E stands for $\sim$ -- in case the link is not clickable. In
%% case of acceptance, we will make our code available to the scientific
%% community via a stable webpage.}

\subsection{Datatypes: Location Specific Data and Messages}
%%%Topology and control/rbc tables.
\input{lsd.tex}
\input{messages.tex}

\subsection{Instantaneously Reacting Sub-Systems}
\label{ssec:instan}

The processing time of controller, interlocking, and RBC is negligible
compared to the time that it takes a train to pass a track. Thus, in
our modelling we assume that these three components react
instantaneously. In Maude this is expressed by saying that these
components do not pose any time constrains. Here, written for the
controller:
%
\begin{lstlisting}[columns=fixed]
eq mte(< O1 : Controller | >) = INF .
\end{lstlisting} 

\vspace{1ex}
\noindent
{\bf Controller.}
\input{controller.tex} 

\vspace{1ex}
\noindent
{\bf Interlocking.}
\input{interlocking.tex} 

\vspace{1ex}
\noindent
{\bf RBC.}
\input{rbc.tex}

%%%Time Dependant Reacting Sub-Systems
\subsection{Trains}
\input{trains.tex}

\subsection{Safety Condition}
\label{sec:safetycondmodelling}
\input{collisionfreedom.tex}


